---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# generalconference

[General Conference](https://www.churchofjesuschrist.org/study/general-conference?lang=eng) is a semi-annual event where members of The Church of Jesus Christ of Latter-day
Saints gather to listen to church prophets, apostles, and other leaders.

This package both scrapes General Conference talks and provides all talks
in a data package. 

```{r, message = FALSE}
library(generalconference)
library(dplyr)
library(tidyr)
```

Load the General Conference corpus, which is a tibble with nested data
for each conference, session, talk, and paragraph.
```{r}
data("genconf")
head(genconf)
```

Unnest it to analyze individual talks, which can be unnested further to
the paragraph level.

```{r}
genconf %>%
  unnest(sessions) %>%
  unnest(talks) %>%
  head()
```

See [Example Analysis](https://bryanwhiting.github.io/generalconference/docs/articles/example-analysis.html) for more examples on how to analyze the data.

See documentation for scrapers, if you need them. But you shouldn't need them since all the data is available.
